---
title: "Exploratory Data Analytics Final Report Akshay Sabade"
author: "Akshay Sabade"
date: "June 16, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Initialize the Required Libraries
```{r}
library(C50)
library(naivebayes)
library(caret)
library (gmodels)
library (MASS)
library(robustbase)
library(tidyverse)
library(kernlab)
library(rpart)
library(rpart.plot)
library(ggplot2)
library(yarrr)
```

```{r}
gapminder <- read.csv("~/Harrisburg University/Anly 506/gapminder.csv")
str(gapminder)
```

```{r echo = FALSE}
r)summary(gapminde
```

```{r}
head(gapminder)
```

```{r}
hist(gapminder$life)
```

```{r echo = TRUE}
table(gapminder$Country)
```



```{r echo = TRUE}
hist(gapminder$Year)
```

```{r echo = FALSE}
data <- data.frame(gapminder)
class(data)
```


```{r}
```


#No of variables
#attributes

```{r echo = FALSE}
NumberofVariables <- ncol(gapminder)
Attributes <- sapply(gapminder, class)
Observations <- nrow(gapminder)
```



#There are 6 variables in the data set.

#There are 4208 of observations in the data set.


```{r echo = FALSE}

sapply(gapminder, function(x) sum(is.na(x)))
sapply(gapminder, function(x) sum(is.na(x)))

```

# Removing the missing values

```{r echo = FALSE}
gapminder <- na.omit(gapminder)
```

## Questions to Answer
  
1. What is the mean life expectan?
  
2. various regions life expentancy sudden increase?
  
3. Is there a relation between life expentancy and income?


```{r echo = FALSE}
Trend <- ggplot(gapminder) + geom_smooth(aes(Year, life))

LifeTrend <- Trend + labs(title = "Relationship between life expectancy and time", subtitle = "Figure 1: Increase in life expetancy", x = "Year", y = "Life Expectancy")
LifeTrend
```












## 2. Various regions life expentancy sudden increase?



```{r echo = FALSE}

gapminder %>%
  
  group_by(region, Year) %>%
  
  summarise(life=median(life)) %>%
  
  ggplot(aes(x=Year, y=life, color=region)) +
  
  geom_line(size=1) + 
  
  geom_point(size=1.5)+ labs(title = "Life expectancy over time", subtitle = "Figure 6", x = "Life", y = "Years")



```



## 3. Relationship between life expectancy and Income

```{r echo = FALSE}

Life <- ggplot(data=gapminder,
                      
                      aes(x=income, y=life))

Life+ geom_point(aes(color=region)) +
  
  geom_smooth(method="loess") + labs(title = "Life expectancy for different continents over time", subtitle = "Life Expectancy and Income.", x = "Life", y = "Years")
Life
```


#COnclusion -> There is DIrect relationship between income and life expentancy

